Supermassive black holes and host bulges affairs -- \\ II. The red and the blue sequences in the mass -- mass diagram.

### 2015-04-26 papers/MbhMsph/mm.tex
mon morn

\subsection{Black hole mass -- galaxy luminosity}
Figure \ref{fig:mbhmaggal} illustrates the $M_{\rm BH} - L_{\rm gal}$ diagram.
Four spiral galaxies had their total luminosities underestimated (see Section \ref{sec:data}) 
and thus are not included in the linear regression analysis. 
Upon analyzing a sample of 35 galaxies, among which only four were classified as spiral galaxies, 
\cite{lasker2014anal} claimed that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations, 
which they fit with a single power-law, have consistent intrinsic scatter.
Here, instead, thanks to our double-sized galaxy sample that includes 17 spiral galaxies, 
we show that the claim made by \cite{lasker2014anal} is valid only for early-type galaxies. 
The $M_{\rm BH} - L_{\rm sph}$ correlation for all galaxies, irrespective of their morphological type, 
has intrinsic scatter $\epsilon_{(Y|X)} = 0.51 \pm 0.06\rm~dex$ (direct linear regression) 
and $\epsilon_{(X|Y)} = 0.60 \pm 0.09\rm~dex$ (inverse linear regression), 
whereas the $M_{\rm BH} - L_{\rm gal}$ correlation for all galaxies has $\epsilon_{(Y|X)} = 0.63 \pm 0.07\rm~dex$ 
and $\epsilon_{(X|Y)} = 0.91 \pm 0.17\rm~dex$.
When considering only early-type galaxies, 
we find that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations have the same level of intrinsic scatter 
($\epsilon_{(Y|X)} = 0.41 \pm 0.06\rm~dex$ and $\epsilon_{(X|Y)} = 0.51 \pm 0.10\rm~dex$ 
against $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$ and $\epsilon_{(X|Y)} = 0.53 \pm 0.10\rm~dex$).
{\bf We point out here that this result does not strongly depend on the value that we assumed for the uncertainty of galaxy magnitudes (0.25). 
In fact, we tested different values and found that we need $error >= 0.7 mag$ to say that gal lum has smaller intrinsic scatter.

From the observer's perspective, measuring galaxy luminosities is obviously easier and faster 
than performing galaxy decompositions to obtain bulge luminosities. 
This, combined with the results from our analysis, suggests that one should prefer the galaxy luminosity over the bulge luminosity 
to predict black hole masses in a sample of elliptical and lenticular galaxies only.

@@

\section{Conclusions}
\label{sec:concl}
ngc0524 outlier, n1332 non outlier

@@

\bibliography{/Users/gsavorgnan/Dropbox_notsync/giulia_e_basta/Literature/SMBHbibliography}

>>>>

\subsection{Black hole mass -- galaxy luminosity}
Figure \ref{fig:mbhmaggal} illustrates the $M_{\rm BH} - L_{\rm gal}$ diagram.
Four spiral galaxies had their total luminosities underestimated (see Section \ref{sec:data}) 
and thus are not included in the linear regression analysis. \\
Upon analyzing a sample of 35 galaxies, among which only four were classified as spiral galaxies, 
\cite{lasker2014anal} claimed that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations, 
which they fit with a single power-law, have consistent intrinsic scatter.
Here, instead, thanks to our double-sized galaxy sample that includes 17 spiral galaxies, 
we show that the claim made by \cite{lasker2014anal} is valid only for early-type galaxies. 
The $M_{\rm BH} - L_{\rm sph}$ correlation for all galaxies, irrespective of their morphological type, 
has intrinsic scatter $\epsilon_{(Y|X)} = 0.51 \pm 0.06\rm~dex$ (direct linear regression) 
and $\epsilon_{(X|Y)} = 0.60 \pm 0.09\rm~dex$ (inverse linear regression), 
whereas the $M_{\rm BH} - L_{\rm gal}$ correlation for all galaxies has $\epsilon_{(Y|X)} = 0.63 \pm 0.07\rm~dex$ 
and $\epsilon_{(X|Y)} = 0.91 \pm 0.17\rm~dex$.
However, when considering only early-type galaxies, 
we find that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations have the same level of intrinsic scatter. 
%($\epsilon_{(Y|X)} = 0.41 \pm 0.06\rm~dex$ and $\epsilon_{(X|Y)} = 0.51 \pm 0.10\rm~dex$ 
%against $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$ and $\epsilon_{(X|Y)} = 0.53 \pm 0.10\rm~dex$).
Because the value of the intrinsic scatter depends on the uncertainties associated to the luminosities\footnote{The 
smaller (larger) the uncertainties, the larger (smaller) the intrinsic scatter.}, 
we tested the robustness of our last conclusion by increasing/decreasing the errors associated to $L_{\rm gal}$ 
(that we originally assumed to be $0.25\rm~mag$) and repeating the linear regression analysis. 
On the other hand, the uncertainties associated to $L_{\rm sph}$ have been estimated 
with an advanced method that takes into account the systematic errors related to the galaxy decomposition process. 
We consider these uncertainties trustworthy and, therefore, we decided to vary only the errors associated to $L_{\rm gal}$.
We found that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations for early-type galaxies 
have inconsistent intrinsic scatter when assuming an error $\geq 0.7\rm~mag$ on $L_{\rm gal}$. 
Because such error is larger than the typical error on $L_{\rm sph}$ used here
-- and, in general, is significantly larger than the uncertainties on $L_{\rm gal}$ that are typically used in the literature --, 
we come to the conclusion that our determination of the intrinsic scatter is reliable, 
and that, for early-type galaxies, $M_{\rm BH}$ correlates equally well with $L_{\rm sph}$ and $L_{\rm gal}$.
As \cite{lasker2014anal} pointed out, from the observer's perspective, measuring galaxy luminosities is obviously easier and faster 
than performing accurate %galaxy decompositions to obtain bulge luminosities. 
This, combined with our last conclusion, suggests that one should prefer the galaxy luminosity over the bulge luminosity 
to predict black hole masses when dealing with samples of elliptical and lenticular galaxies only.

@@

\section{Conclusions}
\label{sec:concl}
%ngc0524 outlier, n1332 non outlier

@@

\bibliography{/Users/gsavorgnan/galaxy_vivisection/papers/SMBHbibliography}
